---
title: "The Actuary and IBNR and IBNYR and IBNER"
variant: markdown_github
bibliography: bibliography.bib
output:
  revealjs::revealjs_presentation:
    css: revealOpts.css
    theme: solarized
    transition: slide
    reveal_options:
      slideNumber: true
      previewLinks: true
  tufte::tufte_handout: default
---

```{r include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
```

```{r}
library(pander)
library(dplyr)
```

# The problem

## The problem

* Split total reserve into IBNYR and IBNER
* The problem is with our _data_ not our algorithms
* Stochastic process for individual claims
* 

## What I'll show you

* Detailed walk through of an example first proposed by Guszcza and Lommele.
* Comment on how this fits with aggregate methods
    * Bifurcated data
    * Hierarchical models
    * Bayesian
* Easy stan walk through
* Stan for individual claims

## What I won't talk about:

* 

# Tiny bit of history

# Toy Example

```{r echo=FALSE}
load("ToyExample.rda")
```

## The parameters

## First cut

```{r echo = FALSE, results='asis'}
# dfTri <- dfTri %>% 
#   mutate(AY = as.character(AY))
# pandoc.table(dfTri, big.mark = ",", missing = "", style = 'rmarkdown')
```

This is painfully easy to develop. So what's the big deal?

## Here's the (soon-to-be) big deal

* For starters, we have no idea about the split between IBNYR and IBNER. The 12-24 month development is a combination of the two.
* Our losses were not stochastic. Imagine a scenario where a claim was reported on January 1 rather than January 31. [Hang on, though. This would put that claim as a first report @24 months claim.]
* What's significant is that there are differences between initial report X and initial report Y.
* The number of claims reported to date is _always_ IBNYR.
* We can regress on the number of open claims. Our intuition tells us that IBNER and IBNYR have have different relationships. 
    * IBNER is positively correlated to open claims. As open claims goes down, incremental development also goes down.
    * IBNYR may have an inverse relationship at earlier development stages. Fewer claims means that I'm going to see more reported.
  * We may now model independently. For more recent periods, we may posit a model for the number of claims, which utilizes our IBNER factors estimated from a prior period.

##

IBNYR

```{r results='asis'}
# pandoc.table(dfTriIBNYR, big.mark = ",", missing = "")
```

IBNER

```{r results='asis'}
# pandoc.table(dfTriIBNER, big.mark = ",", missing = "")
```

# Not-so toy example

##

* 

# Final thoughts

## Why aren't you fitting individual claims?

* I would love to, but honestly, I rarely see actuaries care about doing that.
* This method is a ready analogue to established techniques and can hopefully serve as an on-ramp for actuaries to:
    1. Complain about how much data they're throwing away and 
    2. Move the focus to individual claims

## When does this make sense mathematically?

* When the financial amount (payment or reserve) depends meaningfully on intial or later report
* When the initial amount depends meaningfully on _when_ it is initial

## When does this make sense practically?

* 

## Read everything here:

http://pirategrunt.com/CLRS2017/IBNYER

## References

